Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-05-30 manuscript.tex
Section 5 finished

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 2.5in]{RV_comparison_FACULAE.pdf} 
%\includegraphics[height = 2.5in]{RV_se_comparison_FACULAE.pdf} 
\caption{RV's changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star. SN mean RV seems to have the smallest spurious variations caused by the faculae.}
   %\caption{(left) RV's changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star. SN mean RV seems to have the smallest spurious variations caused by the faculae. (right) Evaluation of the standard errors corresponding to the defined RVs. The standard errors retrieved for SN median RV are $10 \%$ smaller than the standard errors derived for RV. SN mean RV has the largest related uncertainties.}
    \label{fig:faculae}
\end{figure*}

@@

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 2.5in]{RV_comparison_SPOT.pdf} 
%\includegraphics[height = 2.5in]{RV_se_comparison_PLANET_SPOT.pdf} 
\caption{RV's changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star. SN mean RV seems to have the smallest spurious variations caused by the faculae.}
   %\caption{(left) RV's changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star. SN mean RV seems to have the smallest spurious variations caused by the faculae. (right) Evaluation of the standard errors corresponding to the defined RVs. The standard errors retrieved for SN median RV are $10 \%$ smaller than the standard errors derived for RV. SN mean RV has the largest related uncertainties.}
    \label{fig:spot}
\end{figure*}

@@

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 2.5in]{RV_comparison_SPOT_PLANET.pdf} 
%\includegraphics[height = 2.5in]{RV_se_comparison_SPOT.pdf} 
 \caption{RV's changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected. N mean RV seems to have the largest variations caused by the combined action of spot and planet.}
   %\caption{(left) RV's changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected. N mean RV seems to have the largest variations caused by the combined action of spot and planet. (right) Evaluation of the standard errors corresponding to the defined RVs. The standard errors retrieved for SN median RV are $10 \%$ smaller than the standard errors derived for RV. SN mean RV has the largest related uncertainties.}
    \label{fig:spot.plus.planet}
\end{figure*}

@@

\xavier{ To rediscuss with the new values. However, we note that when using SN mean RV, the correction is more important. In fact, the comparison of $R^2$ shows that the SN fit accounts for a higher percentage of variability caused by stellar activity (i.e. spurious variations in RV's). We note also that the BIS SPAN is not helpful to address part of the spurious variability caused by stellar activity, while the opposite conclusion has reached when evaluating the p-value related to $\gamma$.

\begin{figure} 
   \centering
\includegraphics[height = 6in]{NEW_CORRECTIONHD12862_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Set of RV's for Alpha Centauri B using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq. \ref{eq:RV:correction}. Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
   \label{fig:alphacent:correctionRV}
\end{figure}

@@

Both the proposed indicators coming from the SN density have advantages and limits: SN mean RV better catches changes in the asymmetry of the CCF but the resulting set of RV's ends up being contaminated by those spurious shifts caused by stellar activity that have been shortly presented in Sec. \ref{intro}. When using SN median RV, the final set of RV's is less affected by those spurious shifts caused by stellar activity, but at the same time this indicator is not able to catch as well as SN mean RV changes in the shape and in the width of the CCF. Once corrected from stellar activity using Eq.~\ref{eq:RV:correction}, the results are comparable. Anyway, both SN mean RV and SN median RV are useful to catch different aspects of the CCF and our suggestion is to use SN mean RV when interested in retrieving information about changes in the shape and/or the width of the CCF. In order to provide a set of RV's containing the smallest amount of spurious contamination imputable to stellar activity (i.e. before to run Eq.~\ref{eq:RV:correction}), our suggestion is to use instead SN median RV.

@@

We also consider a real-data example using HARPS spectra from the star Alpha Centauri B with an imputed Doppler-shift added...

\umberto{to be done}\xavier{to plot K vs P for Normal, SN mean, SN median}

In the next Section we further motivate the reasons to define the RV's derived by the CCF by calculating SN median RV. In order to do that, we retrieve the standard errors associated with SN mean RV, SN median RV and RV.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Estimation of standard errors for the CCF parameters} \label{sec:5}

In this Section, we perform a bootstrap analysis \citep{davison1997bootstrap, efron1994introduction} in order to retrieve the standard errors associated to SN mean RV, SN median RV, RV, SN FWHM, FWHM, $\gamma$ and BIS SPAN. Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other. Therefore, we cannot do a bootstrap analysis on perturbing independently each CCF point with a Normal density scaled to the error of each given point. A detailed discussions of the methods nowadays available to resampling in situations with dependent data structures is available in \citet{lahiri2013resampling}. All the bootstrap methods that deal with dependant data structures rely on the so called Block Bootstrap methods, originally introduced by \citet{wilks1997resampling}. In our particular case, since each point in a CCF is correlated with each other, we bootstrap a hundred times the stellar spectrum given the photon-noise error of each wavelength and calculate for each realization a new CCF. We then fit a Normal or a SN density to each of these CCF's and then calculate the standard deviations of the density for the location parameters (RV, SN mean RV or SN median RV), the width parameters (SN FWHM or FWHM ) and the asymmetry parameters ($\gamma$ or BIS SPAN).

>>>>

\begin{figure}[htbp]
   \centering
\includegraphics[width=3.6in]{RV_comparison_FACULAE.pdf} 
%\includegraphics[height = 2.5in]{RV_se_comparison_FACULAE.pdf} 
\caption{RV's changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star. SN mean RV seems to have the smallest spurious variations caused by the faculae.}
   %\caption{(left) RV's changes as function of the orbital phase in the case in which a faculae is present on the photosphere of the star. SN mean RV seems to have the smallest spurious variations caused by the faculae. (right) Evaluation of the standard errors corresponding to the defined RVs. The standard errors retrieved for SN median RV are $10 \%$ smaller than the standard errors derived for RV. SN mean RV has the largest related uncertainties.}
    \label{fig:faculae}
\end{figure}

@@

\begin{figure}[htbp]
   \centering
\includegraphics[width=3.6in]{RV_comparison_SPOT.pdf} 
%\includegraphics[height = 2.5in]{RV_se_comparison_PLANET_SPOT.pdf} 
\caption{RV's changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star. SN mean RV seems to have the smallest spurious variations caused by the faculae.}
   %\caption{(left) RV's changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star. SN mean RV seems to have the smallest spurious variations caused by the faculae. (right) Evaluation of the standard errors corresponding to the defined RVs. The standard errors retrieved for SN median RV are $10 \%$ smaller than the standard errors derived for RV. SN mean RV has the largest related uncertainties.}
    \label{fig:spot}
\end{figure}

@@

\begin{figure}[htbp]
   \centering
\includegraphics[width = 3.6in]{RV_comparison_SPOT_PLANET.pdf} 
%\includegraphics[height = 2.5in]{RV_se_comparison_SPOT.pdf} 
 \caption{RV's changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected. N mean RV seems to have the largest variations caused by the combined action of spot and planet.}
   %\caption{(left) RV's changes as function of the orbital phase in the case in which a spot is present on the photosphere of the star and a planet is injected. N mean RV seems to have the largest variations caused by the combined action of spot and planet. (right) Evaluation of the standard errors corresponding to the defined RVs. The standard errors retrieved for SN median RV are $10 \%$ smaller than the standard errors derived for RV. SN mean RV has the largest related uncertainties.}
    \label{fig:spot.plus.planet}
\end{figure}

@@

\xavier{When looking at the significance of the different parameters in the activity correction in Table~\ref{table:alphacent.test}, we see that the intercept is not significant for any of the correction, and BIS SPAN, with coefficient $\beta_2$, is not useful to explain stellar activity when using the parameters derived from the Normal density fit. However all the other parameters in the Normal and SN case are useful. By analyzing the value for $R^2$, we see that the correction is more efficient at explaining stellar activity when considering for the CCF barycenter SN mean RV. This is expected from the results above since for the three different cases, we arrive to the same RV residual rms after correction, but before correction SN mean RV shows the largest RV rms.}

\begin{figure*} 
   \centering
\includegraphics[height = 6in]{NEW_CORRECTIONHD12862_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Set of RV's for Alpha Centauri B using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq. \ref{eq:RV:correction}. Once corrected for stellar activity, the residuals in the Normal and SN analyses are comparable.}
   \label{fig:alphacent:correctionRV}
\end{figure*}

@@

%Both the proposed indicators coming from the SN density have advantages and limits: SN mean RV better catches changes in the asymmetry of the CCF but the resulting set of RV's ends up being contaminated by those spurious shifts caused by stellar activity that have been shortly presented in Sec. \ref{intro}. When using SN median RV, the final set of RV's is less affected by those spurious shifts caused by stellar activity, but at the same time this indicator is not able to catch as well as SN mean RV changes in the shape and in the width of the CCF. Once corrected from stellar activity using Eq.~\ref{eq:RV:correction}, the results are comparable. Anyway, both SN mean RV and SN median RV are useful to catch different aspects of the CCF and our suggestion is to use SN mean RV when interested in retrieving information about changes in the shape and/or the width of the CCF. In order to provide a set of RV's containing the smallest amount of spurious contamination imputable to stellar activity (i.e. before to run Eq.~\ref{eq:RV:correction}), our suggestion is to use instead SN median RV.

@@

\xavier{In the preceding section, we saw that the RV measured when considering a SN or a Normal density present different amplitudes, mainly in the case of SN mean RV. However, when correcting for stellar activity using the linear combination presented in Eq.~\ref{eq:RV:correction}, it seems that we are able to reach the same RV precision. In this section, we want to investigate if for some of the three different RV definitions presented in this paper, it is easier or more difficult to detect planetary signals when considering stellar activity. To do so, we estimated what would be the minimum amplitude of a planetray signal we could detect at different orbital periods.

To get CCF affected by realistic stellar activity signals, we took the ones from Alpha Cen B used in the preceding section. To simulate a planetary signal, when then blue- or red-shifted those CCF with the wanted amplitude, period and phase.

We first simulated several RV data sets, with always the same stellar signal, but injecting planets with parameters corresponding to the following grid:
\begin{itemize}
\item period of 3, 5, 7, 9, 11, 15, 20 , 25 and 30 days,
\item amplitude from 0.5 to 3 \ms\, by steps of 0.05\,\ms,
\item 10 different phases, evenly sampled between 0 and 2$\pi$.
\end{itemize}

For each simulation, 4500 in total, we applied the activity correction presented in Eq.~\ref{eq:RV:correction} and look for signals in the residuals using a Generalized Lomb-Scargle periodogram \citep[GLS][]{Zechmeister-2009}. If a signal with a p--value\footnote{estimated by bootstrap} smaller than 1\% had a period compatible with the injected planetary period considering an error of 20\%, we were estimating this signal as significant, and therefore the corresponding planet as detected.

Finally, for each period, we searched for the minimum amplitude for which at least 50\% of the planets with different phases were detected. The results are shown in Fig.~\ref{fig:detection_limits.pdf}. As we can see, all the different RV estimates gives extremely similar detection limits. Therefore, we can use any of these estimates when searching for planetary signal in RV data contaminated by stellar activity.

Although the detection limits stay constant for nearly all the periods, we see that for 30 days, we have a huge increase for all the RV estimates. This is because the planet period is close to the rotation period of the star \citep[36.7 days,][]{Dumusque-2012}, and therefore close to the semi-periodicity of the stellar activity signal. In such a case, the activity correction absorbs part of the planetary signal. We thus need to inject a much stronger planetary signal at this period if we want to detect it.}

%-----------------------------------------------------------------------------------------------------------------------------------------------
\section{Estimation of standard errors for the CCF parameters} \label{sec:5}

\xavier{In this section, Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other. Therefore, we cannot simply shuffle each point in the CCF with their respective error bar and then recalculate the best SN or Normal density fit, to see how the noise of the CCF influence the noise on the parameters derived from the CCF. We therefore decided to start with the spectrum, for which we know that each points are totally independent of the others. The standard error on each point is given by the photon noise, which follows a Poisson law and is therefore the square root of the measured flux.}

In this Section, we perform a bootstrap analysis \citep[e.g.][]{davison1997bootstrap, efron1994introduction} in order to retrieve the standard errors associated to SN mean RV, SN median RV, RV, SN FWHM, FWHM, $\gamma$ and BIS SPAN. Because a CCF is obtained from a cross-correlation, each point in a CCF is correlated with each other. Therefore, we cannot do a bootstrap analysis on perturbing independently each CCF point with a Normal density scaled to the error of each given point. A detailed discussions of the methods nowadays available to resampling in situations with dependent data structures is available in \citet{lahiri2013resampling}. All the bootstrap methods that deal with dependant data structures rely on the so called Block Bootstrap methods, originally introduced by \citet{wilks1997resampling}. In our particular case, since each point in a CCF is correlated with each other, we bootstrap a hundred times the stellar spectrum given the photon-noise error of each wavelength and calculate for each realization a new CCF. We then fit a Normal or a SN density to each of these CCF's and then calculate the standard deviations of the density for the location parameters (RV, SN mean RV or SN median RV), the width parameters (SN FWHM or FWHM ) and the asymmetry parameters ($\gamma$ or BIS SPAN).
